Resolving Limits Faced by Classical Machine Learning Approaches: Areas of Application for Collaborative Interactive Learning Techniques

### 2018-08-11 paper.tex
Restructure the sections

\section{Introduction}\label{sec:intro}
\notes{[Introduction is too long, the examples shouldn't be in the introduction in detail.--> extra section]}
As with most concepts, there is no canonical 
definition for the term \textit{Machine Learning (ML)} but at its most basic form it 
can be described as algorithms that learn from a given set of training examples 
$\{(x_i, y_i)\}$ of inputs $x_i$ and outputs $y_i$ in order to 
make predictions on unknown input data. According to Tom 
Mitchell, a computer scientist from Carnegie Mellon University,  ML tries 
to answer how we can build algorithms that automatically improve through 
experience and which fundamental laws govern all these learning processes\cite{ML:mitchell}.
The area of ML in general is a fast-growing discipline at the intersection of statistics 
and computer science and has experienced massive research interest in the last decades.
With its various application possibilities it has also been an interesting branch for 
economists and entrepreneurs.
Since ML scenarios like \textit{supervised}, \textit{unsupervised} and 
\textit{semi-supervised} learning, which we will cover later, are heavily data-driven, 
the internet with its massive amount of data has contributed to the further development 
of research in the area of fully automated learning algorithms. Today, we can see the 
results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell}, 
not limited to the list below.
\begin{itemize}
    \item \textit{Text classification, Natural Language Processing (NLP)}. 
        Many current mail programs have built-in spam detection which originally used
        simple regular expressions in order to detect phrases commonly used in spam mails.
        With state-of-the-art ML techniques it is not only possible for a mail program to 
        query for a number of words but to recognise patterns of how spam mails are constructed and 
        to adapt itself to new types of spam.
    \item \textit{Speech recognition}. 
        Most commercial applications for speech recognition also use ML to train itself to 
        recognise a user's speech input in order to perform further semantic analysis on
        that data.
    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
        Machine Learning methods have also been successfully applied in domains where it's 
        important to extract information from images such as detecting and classifying 
        objects or recognizing handwritten characters. Image 
        recognition and OCR are therefore for example used in medical diagnosis to 
        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
        stay on track or in post-offices to sort envelopes with hand-written addresses
        \cite{DisciplineOfML:mitchell}.
    \item \textit{Games}.
        Computer Games usually offer a Multiplayer mode where a user can interact and 
        play the game even without a human opponent. For games with a small number of 
        possible moves after each turn, and therefore a relatively small game tree containing 
        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
        It figures out which next move would minimize the worst-case scenario for all subsequent 
        moves. Therefore, it needs to know all possible moves, which can easily become computationally 
        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
        250 (AlphaGo) possible subsequent game states.
        In order to still have challenging opponents, modern Games are using ML to gain experience 
        by themselves.
    \item \textit{Search engines, Recommendation systems}.
        Nearly all current search machines use ML in one fashion or another. They mainly use these 
        techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
        search results and for \textit{(2) Query classification} in order to ``understand' a 
        users query and to provide further meaningful information.
\end{itemize}

Despite the successful application of ML in a lot of fields, most of these examples 
need a sufficient amount of labeled training data ($x_i$ with assigned $y_i$) in order to make 
correct predictions on, or discover structured patterns in unknown data $x_j$. However, most 
data sets in the biomedical domain, in robotics or in other fields, where data is collected 
from sensor systems or other unreliable sources, often are either not available (e.g.\ rare 
diseases, borderline cases in road traffic, \dots) or contain noisy data, dirty data or unwanted 
data due to dirty sensors or poor visibility conditions in camera applications.
In addition, a machine learning algorithm's prediction is solely based on the training data it 
has seen before. One might argue that human decisions are also only based on experience having been
made since their childhood but humans are often still superior to most algorithms in terms of 
the instinctive interpretation of complex patterns. Furthermore, they can learn to recognize 
structural patterns from very few training data.

\begin{figure}[!h]
\centering
\includegraphics[width=3.5in]{images/CIL}
\caption{Collaborative Interactive Learning.}
\label{fig:CIL}
\end{figure}

Hence, \textit{Collaborative Interactive Learning (CIL)} includes domain experts (humans) 
and other CIL systems in the decision/prediction making process as shown in 
Figure~\ref{fig:CIL}. The relatively new term describes a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and the one of other entities in a 
        bi-directional way\cite{CIL:sick}.
\end{itemize}

This article gives a brief introduction on possible areas of application for the CIL-approach. 
It starts with an overview of classical machine learning scenarios, discussing where they are 
facing limits, describing the relation to Organic Computing and motivating the use of CIL\@. 
It then lists possible applications and concludes 
with a view on future research interests.

\section{Algorithmic Foundations}
Before we take a closer look at the applications and challenges of CIL, let's first consider the 
following existing machine learning strategies and algorithms. As already mentioned above, 
there is a multitude of definitions for the term ML\@. But primarily, Arthur Samuel 
coined this term in 1959. Of course, a lot has changed in this area since then, 
however, the definition that ML allows computers to solve problems without being 
specifically programmed to do so, is still valid today\cite{MLStudiesUsingCheckers:samuel}.

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different approaches 
for that\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
In the following section I want to present five strategies\cite{FoundationsOfML:mohri}.
\notes{[Add examples for each classification.]}

@@

>>>>

\section{Introduction}\label{sec:intro}
As with most concepts, there is no canonical 
definition for the term \textit{Machine Learning (ML)} but at its most basic form it 
can be described as algorithms that learn from a given set of training examples 
$\{(x_i, y_i)\}$ of inputs $x_i$ and outputs $y_i$ in order to 
make predictions on unknown input data. According to Tom 
Mitchell, a computer scientist from Carnegie Mellon University,  ML tries 
to answer how we can build algorithms that automatically improve through 
experience and which fundamental laws govern all these learning processes\cite{ML:mitchell}.
The area of ML in general is a fast-growing discipline at the intersection of statistics 
and computer science and has experienced massive research interest in the last decades.
With its various application possibilities it has also been an interesting branch for 
economists and entrepreneurs.
Since ML scenarios like \textit{supervised}, \textit{unsupervised} and 
\textit{semi-supervised} learning, which we will cover later, are heavily data-driven, 
the internet with its massive amount of data has contributed to the further development 
of research in the area of fully automated learning algorithms. Today, we can see the 
results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell} 
described in more detail in Section~\ref{sec:algos}.

% List with current ML applications

Despite the successful application of ML in a lot of fields, most of these examples 
need a sufficient amount of labeled training data ($x_i$ with assigned $y_i$) in order to make 
correct predictions on, or discover structured patterns in unknown data $x_j$. However, most 
data sets in the biomedical domain, in robotics or in other fields, where data is collected 
from sensor systems or other unreliable sources, often are either not available (e.g.\ rare 
diseases, borderline cases in road traffic, \dots) or contain noisy data, dirty data or unwanted 
data due to dirty sensors or poor visibility conditions in camera applications.
In addition, a machine learning algorithm's prediction is solely based on the training data it 
has seen before. One might argue that human decisions are also only based on experience having been
made since their childhood but humans are often still superior to most algorithms in terms of 
the instinctive interpretation of complex patterns. Furthermore, they can learn to recognize 
structural patterns from very few training data. Hence, a new approach is needed in order to 
counteract the disadvantages of classical ML\@.
This article gives a brief introduction on possible areas of application for 
\textit{Collaborative Interactive Learning (CIL)}. It starts with an overview of classical 
machine learning scenarios, discussing where they are facing limits, describing the relation 
to Organic Computing and motivating the use of CIL\@. It then lists possible applications 
and concludes with a view on future research interests.

\section{Collaborative Interactive Learning}\label{sec:cil}
\notes{[More detail.]}
CIL includes domain experts (humans) 
and other CIL systems in the decision/prediction making process as shown in 
Figure~\ref{fig:CIL}. The relatively new term describes a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and the one of other entities in a 
        bi-directional way\cite{CIL:sick}.
\end{itemize}
\begin{figure}[!h]
\centering
\includegraphics[width=3.5in]{images/CIL}
\caption{Interaction between heterogeneous systems in CIL.}
\label{fig:CIL}
\end{figure}

\section{Algorithmic Foundations}
\label{sec:algos}
Before we take a closer look at the applications and challenges of CIL, let's first consider the 
following existing machine learning strategies and algorithms. As already mentioned above, 
there is a multitude of definitions for the term ML\@. But primarily, Arthur Samuel 
coined this term in 1959. Of course, a lot has changed in this area since then, 
however, the definition that ML allows computers to solve problems without being 
specifically programmed to do so, is still valid today\cite{MLStudiesUsingCheckers:samuel}.

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different approaches 
\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
However, in the following section I want to present five common strategies\cite{FoundationsOfML:mohri}.
\notes{[Add examples for each classification.]}

@@

\begin{itemize}
    \item \textit{Text classification, Natural Language Processing (NLP)}. 
        Many current mail programs have built-in spam detection which originally used
        simple regular expressions in order to detect phrases commonly used in spam mails.
        With state-of-the-art ML techniques it is not only possible for a mail program to 
        query for a number of words but to recognise patterns of how spam mails are constructed and 
        to adapt itself to new types of spam.
    \item \textit{Speech recognition}. 
        Most commercial applications for speech recognition also use ML to train itself to 
        recognise a user's speech input in order to perform further semantic analysis on
        that data.
    \item \textit{Image recognition, Optical Character Recognition (OCR)}.
        Machine Learning methods have also been successfully applied in domains where it's 
        important to extract information from images such as detecting and classifying 
        objects or recognizing handwritten characters. Image 
        recognition and OCR are therefore for example used in medical diagnosis to 
        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
        stay on track or in post-offices to sort envelopes with hand-written addresses
        \cite{DisciplineOfML:mitchell}.
    \item \textit{Games}.
        Computer Games usually offer a Multiplayer mode where a user can interact and 
        play the game even without a human opponent. For games with a small number of 
        possible moves after each turn, and therefore a relatively small game tree containing 
        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
        It figures out which next move would minimize the worst-case scenario for all subsequent 
        moves. Therefore, it needs to know all possible moves, which can easily become computationally 
        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
        250 (AlphaGo) possible subsequent game states.
        In order to still have challenging opponents, modern Games are using ML to gain experience 
        by themselves.
    \item \textit{Search engines, Recommendation systems}.
        Nearly all current search machines use ML in one fashion or another. They mainly use these 
        techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
        search results and for \textit{(2) Query classification} in order to ``understand' a 
        users query and to provide further meaningful information.
\end{itemize}
